Towards the Internet of Things: A Real-World Testbed

### 2013-06-13 trunk/doc/paper- towards the internet of things/paper v1.tex

\documentclass[conference]{IEEEtran}
\ifCLASSINFOpdf
\else
\fi
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}

\title{Towards the Internet of Things: A Real-World Testbed}
\author{\IEEEauthorblockN{Nacer Khalil}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: n.khalil@aui.ma}
\and
\IEEEauthorblockN{Mohammed Reduane Abid}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: r.abid@aui.ma}
\and
\IEEEauthorblockN{Driss Benhaddou}
\IEEEauthorblockA{School of Engineering and Technology\\
University of Houston\\
Email: dbenhaddou@uh.edu}}
\maketitle
\begin{abstract}
The internet has seen its importance grow exponentially throughout the previous two decades. It has started as set of computers sharing static information written by human beings and accessed by other human beings. It followed mainly the publisher subscriber model. Later on, with the arrival of internet 2.0, the subscriber had now the ability to affect the content at the publisher's level and this basic idea gave rise to a whole new world of applications such as wikis, blogs, social networks and other applications. The next revolution in the internet is the introduction of machines as players within the internet. This will allow the machines to intercommunicate between them or what is known as machine-to-machine communication. More and more devices will be able to communicate and thus be part of the internet. This will give rise to a whole new dimension of possibilities as the focus of the internet will not only be human interactions but also machine interactions. As an example of autonomous machines communicating through, the components of smart grids will be part of the internet of things. Devices such as AMI, smart homes, wireless sensor networks will all be part of the internet of things. Any device within the smart grid will be uniquely identified through the network and therefore will be able to communicate. In this paper, we provide a back-end architecture and a real-world testbed for the smart home communication.
\end{abstract}

@@

\section{Internet of things}

\section{6lowpan}
6loWPAN stands for  "IPv6 over Low power Wireless Personal Area Networks".

\section{Architecture}

@@

\subsection{Network gateway packet transformation}
This is a very component in the system. The issue is the following. The WSN network supports only IPV6 while other components such as the middleware and the mobile client do not necessary have an IPV6 address, but we still want all the components to communicate independently of the IP technology to be used. To do so, we have created a network packet transformation program. This program basically converts IPV4 to IPV6 and vice versa. To do so, it assigns virtual IPV4 addresses to IPV6 address holders and and IPV6 address to IPV4 address holders. With such a program, each player in the network has both an IPV4 and an IPV6 but is aware of only the one that is assigned to him. The other "virtual" address is known only at the level of the program installed at the gateway station between the WSN and the outside world. The flow of information works as follow; when a station wants to send requests to a mote, it will send IPV4 packet holding the request to the mote but by addressing it using its virtual IPV4 address. This packet will be sniffed by this packet transformation 
\section{Measurements}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}

\begin{document}

\title{Towards the Internet of Things: A Real-World Testbed}
\author{\IEEEauthorblockN{Nacer Khalil}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: n.khalil@aui.ma}
\and
\IEEEauthorblockN{Mohamed Riduan Abid}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: r.abid@aui.ma}
\and
\IEEEauthorblockN{Driss Benhaddou}
\IEEEauthorblockA{School of Engineering and Technology\\
University of Houston\\
Email: dbenhaddou@uh.edu}}
\maketitle
\begin{abstract}
The internet has seen its importance grow exponentially throughout the previous two decades. It has started as set of computers sharing static information written by human beings and accessed by other human beings. It followed mainly the publisher subscriber model. Later on, with the arrival of internet 2.0, the subscriber had now the ability to affect the content at the publisher's level and this basic idea gave rise to a whole new world of applications such as wikis, blogs, social networks and other applications. The next revolution in the internet is the introduction of machines as players within the internet. This will allow the machines to intercommunicate between them or what is known as machine-to-machine communication. More and more devices will be able to communicate and thus be part of the internet. This will give rise to a whole new dimension of possibilities as the focus of the internet will not only be human interactions but also machine interactions. As an example of autonomous machines communicating through, the components of smart grids will be part of the internet of things. Devices such as AMI, smart homes, wireless sensor networks will all be part of the internet of things. Any device within the smart grid will be uniquely identified through the network and therefore will be able to communicate. In this paper, we present a real-world testbed for integrating wireless sensors into the internet. The solution uses 6lowPAN, and addresses relevant issues at the level of the gateway. we used legacy hardware and proved communication.
\end{abstract}

@@

\section{Internet of things}
The internet of things is a new concept based on the idea that there will be much more users that are computers, machine than human beings. This means that machines will play an important role in the internet and they will be able to communicate autonomously without the interaction of human beings. Wireless sensor network will be part of the internet of things and therefore will be actively communicating in the internet by sending sensor data. Nowadays, the internet is mainly based on a human-to-human. In the future of internet called the internet of things, we will have in addition to human-to-human communication, human-to-machine communication and machine-to-machine communication. An example of human-to-machine communication is when the human will be able to control the wireless sensor network's sampling time. An example of machine-to-machine communication which will be discussed in this paper is the middleware being able to turn off the light because no one is in the room. The middleware by making use of the sensor data will communicate with motes to turn on or off the light bulb.
\section{6lowpan}
6loWPAN stands for  "IPv6 over Low power Wireless Personal Area Networks". It stands for the name of the working group within IETF. It is based on the idea that all the devices independently of their processing power or energy resources should be able to have the TCP/IP protocol stack and be part of the internet of things. In order to be able to build the TCP/IP protocol stack in low-power devices, there have been multiple aspects of the protocol stack that has to be optimized. As an example, the IP MTU(maximum transmission unit) is fixed at 1280 bytes whereas the Zigbee MTU is only 127 bytes. This means that not every IPV6 packet can be inserted within a Zigbee frame. Another issue is related to the addressing with the 128 bits address. in 6lowpan, the addressing via the IPV6 address is performed hierarchically to first identify is the packet is sent to a device within that network but afterwards, addressing is done by counting mainly on the 16 last bits of the IPV6 address. These were just two of a large set of issues that 6lowpan tries to solve in order to enable even the low-power devices to join the internet of things. TinyOS as being one of the most used operating system comes with its implementation of 6lowpan through a project called BLIP (Berkeley Low-power IP stack) that provides a lightweight implementation of the 6lowpan and that can be installed and used with a variety of motes as long as they support IPV6. This project makes use of BLIP to provide the TCP/IP protocol stack to the devices within the wireless sensor network.
\section{Architecture}
The project is composed of three building blocks. 
\begin{itemize}
\item Wireless sensor network (WSN)
\item Gateway server
\item Middleware
\item Mobile client
\end{itemize}
The WSN communicates using zigbee as well as with the gateway server using IPV6 technology whereas whereas the communication between the gateway server, the middleware and the mobile client is done via Wifi using IPV4 technology. The architecture enables any component within this system to communicate with any other system independently of the communication medium used (Zigbee or Wifi) or the network technology used (IPV4 or IPV6). Figure 1 is a network diagram that depicts the different components of the system as well as the routes that exist for any component to communicate with another.

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{images/network_diagram.jpg}
\caption{Network diagram}
\label{fig:network}
\end{figure}

\subsection{Wireless sensor network}
The wireless sensor network is based on the mesh topology. It is also designed in order to be an ad-hoc network. This means that you can place the mote any where as long as there is one link it can attain to communicate with. The routing is multi-hop and links are created dynamically between different motes of the WSN provided that there frames can reach the destination.

\subsection{Gateway server}
The gateway server is a crucial component within the system. It is responsible for extracting Wifi frames and forwarding them as Zigbee frames and vice versa. It is also responsible for receiving IPV4 packet and transforming them into IPV6 and vice versa. The gateway server has other functionalities which are the ability to receive sensor data from all the motes in the wireless sensor network and forwarding them to the middleware. In case the link between the gateway server and the middleware is lost, the gateway server stores the received data and sends them when the link is up again. This feature serves as a way to avoid losing data.

\subsection{Middleware}
The middleware is a special program that is used to hide the heterogeneity of the system from external users. The middleware also provides automation mechanisms to control and reduce the energy consumption, but the main features are the ability to receive data, filter it, transform it and store it in a coherent fashion in order to make the most of this data and use it smartly to reduce consumption. Concerning the client access, the middleware provides a set of web services that enable the clients to access all sorts of information such as the real-time consumption, daily consumption and other information inferred from the sensor data coming from the wireless sensor network.

\subsection{Mobile client}
The mobile client application is an interactive application for android phones that enable users to get access to the real-time consumption of their homes and also to remotely control their appliance by turning on and off any appliance linked to some mote in the wireless sensor network. The mobile client when wanting to turn on or off some appliance sends a request directly towards the mote responsible for that action and designate the mote using its "vitual" IPV4 address that it does not own in really since it has an IPV6 address but that virtual IPV4 address is reserved for that mote and the translation is dealt with at the level of the gateway.

\ Now that all components have been explained, the data flow of the information is to be explained. As it was stated before, the any component of the system can communicate with any other independently of the data link layer technology or network layer technology.

@@

\subsection{Network gateway packet transformation}
This is a very important component in the system. The issue is the following. The WSN network supports only IPV6 while other components such as the middleware and the mobile client do not necessary have an IPV6 address, but we still want all the components to communicate independently of the IP technology to be used. To do so, we have created a network packet transformation program. This program basically converts IPV4 to IPV6 and vice versa. To do so, it assigns virtual IPV4 addresses to IPV6 address holders and and IPV6 address to IPV4 address holders. With such a program, each player in the network has both an IPV4 and an IPV6 but is aware of only the one that is assigned to him. The other "virtual" address is known only at the level of the program installed at the gateway station between the WSN and the outside world. The flow of information works as follow; when a station wants to send requests to a mote, it will send IPV4 packet holding the request to the mote but by addressing it using its virtual IPV4 address. This packet will be sniffed by this packet transformation program that will extract the TCP datagram from the ip packet, create a new IPV6 packet specifying the source address as the virtual address of the host and the destination as the address of the mote and then append the TCP datagram to the newly created packet and send it to the mote sink packet forwarding component that is seen by the gateway as a network interface card. This leads to a complicated issue that is to be handled and which is that the program should keep track of the request responses in order to forward them correctly to the destination. To solve such a problem, an algorithm has been created whose sole role is to mechanically compute the IPV6 address of the host based on its IPV4 and vice versa. This algorithm is based on function whose primary quality is the fact that it is bijective which means any IPV4 address is mapped to one and only one IPV6 function and vice versa. So whenever a request is coming, the source and destination address will be converted using this algorithm and this will make avoid the whole request response tracking part.
\section{Measurements}
